--- 
title: "MTH017 Linear Algebra for Mathematical Science"
author: ""
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: rstudio/bookdown-demo
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

# Prerequisites

Placeholder



<!--chapter:end:index.Rmd-->

# Introduction {#intro}

You can label chapter and section titles using `{#label}` after them, e.g., we can reference Chapter \@ref(intro). If you do not manually label them, there will be automatic labels anyway, e.g., Chapter \@ref(methods).

Figures and tables with captions will be placed in `figure` and `table` environments, respectively.

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].

<!--chapter:end:01-intro.Rmd-->

# Chapter 1 Linear Equations in Linear Algebra

## Systems of Linear Equations

### Linear System

#### Linear System (线性系统), Coefficient (系数) and Variable (变量)

A linear equation is 
\begin{equation}
    a_1x_1+a_2x_2+\cdots+a_nx_n=b \qquad n=1, 2, 3, \cdots, \infty
\end{equation}
$a_1,\dots,a_n$ are real or complex numbers, called **{coefficient}**.\\
$x_1,\dots,x_n$ are unknown **{variables}**\\
A system of linear equations is called **{linear system}**.\\

```{r}
knitr::include_app("https://yihui.shinyapps.io/miniUI/",
  height = "600px")
```

```{r letter-a, echo=FALSE}
question("What number is the letter A in the English alphabet?",
  answer("8"),
  answer("14"),
  answer("1", correct = TRUE),
  answer("23")
)
```

<!--chapter:end:02-Chapter1.Rmd-->

`r if (knitr:::is_html_output()) '
# References {-}
'`

<!--chapter:end:06-references.Rmd-->

